Jahn-Teller effect with rigid octahedral rotations in perovskites

### 2023-12-25 manuscript/prb-submitted/paper.tex
hopping effects included. references, titles included

\documentclass[a4paper,prb,twocolumn]{revtex4-1}  %a4paper,prb,twocolumn
%\documentclass[preprint]{revtex4-1}

@@

Of course, beside the crystal field we consider in our simplistic model,
in real materials,
 there would be other local effects like
electronic correlations (Hubbard and Hund's interaction)
and spin-orbit interaction, 
as well as band structure effects arising from
the electron hopping between the B ions.
The interplay between these and the crystal field (or JT) effect 
we discussed in this manuscript is also an interesting future work.
However, a few remarks are in order. 
Unlike the electronic correlations and spin-orbit interaction,
 the hybridization between 
the orbitals localized on different B sites are not
rotationally invariant.
Assuming the crystal field splitting to be the largest energy scale,
the orbitals in the $e_g$ and $t_{2g}$ manifolds of B sites are aligned with their respective octahedra,
and
the hybridization between the orbitals localized on different B sites
(and the electronic band structure arising from them)
are modified as the octahedra rotate.

To shed some light on the 
role of these band structure effects,
we consider the nearest neighbor hopping between the B sites
using the Slater-Koster method~\cite{SlaterKoster}
and
calculate the change in the energy of two configurations
$t_{2g}^1$ and $e_g^1$
as the octahedra rotate
in three cases: with either the crystal field or the hopping only and with both of these simultaneously.
Figure~\ref{fig:hybrid}(a)
shows the change in the energy 
as a function of $\beta$ for the first two cases
for the crystal-field-only (black curves, left y-axis;
$\alpha=0$, $q=2q_o$, $\Delta_o=4q_o/15a$)
and for the hopping-only case (red/gray curves, right y-axis).
We use Slater-Koster hopping parameters
$(t_{\sigma},t_{\pi},t_{\delta})=(0.15,-0.1,0.025)$~eV, 
$a=7$~bohr, $q_o=2$~e,
and consider only the crystal field of O octahedra that creates
$t_{2g}$ and $e_g$ manifolds.
While both $t_{2g}^1$ and $e_g^1$ configurations 
show a lowering of energy 
due to
the crystal field 
as $\beta$ 
increases---consistent with the results presented 
before---the energy of $e_g^1$ increases when only hopping is considered 
(the effect scales with the hopping parameters or the bandwidth).
This is due to a reduced hybridization leading to narrower $e_g$ bands.
In contrast, the energy of $t_{2g}^1$ decreases due band widening arising from 
an enhanced hybridization.
The crystal field and these band structure effects are not additive however.
The rotation induced splitting of the $t_{2g}$/$e_g$ manifolds
suppresses the effectiveness of the hopping in creating 
the dispersion in the energy states, 
and thus reduces the bandwidths and
affects the associated rotation induced energetic changes.

To show the validity regime of our crystal field model 
presented in this manuscript,
Fig.~\ref{fig:hybrid}(b)
presents  
the ratio of the
 change in the energy 
at $\beta=20^\circ$ (i.e., the energy difference from the cubic case)
at finite hopping $E(W)$ to that of our simplistic crystal field model $E(0)$
as a function of the average bandwidth $W$ of $t_{2g}$ and $e_g$ bands.
Here we scale the Slater-Koster parameters used for Fig.~\ref{fig:hybrid}(a)
to tune the bandwidth $W$.
We see that $E(W)/E(0)$ decreases from unity at $W=0$
to half its value for $t_{2g}^1$ configuration at $W/\Delta_o\gtrsim0.3$,
and even becomes negative for $e_g^1$ configuration around 
$W/\Delta_o\gtrsim0.15$ (showing the dominance of the band structure effects).
From this analysis, we conclude that the results of our crystal field model 
hold unambiguously only for narrower bands, $W/\Delta_o\ll1$.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.0\linewidth]{hybrid}
\caption{The effect of dispersion due to the electron hopping between B sites.
(a) Energy of two configurations $t_{2g}^1$ and $e_g^1$
as a function of $\beta$ when either the crystal field or the hopping is considered alone.
In the latter case, the energy changes are scaled with the bandwidth $W$.
(b) Considering both the crystal field and the hopping simultaneously,
the ratio of the change in energy with rotation $\beta$ at a finite hopping to that in the absence of hopping $E(W)/E(0)$
as a function of the average bandwidth $W$ 
for the same two configurations
$t_{2g}^1$ and $e_g^1$.
The results of the crystal field model presented in this manuscript 
hold in the small bandwidth limit where $E(W)/E(0)\sim 1$.
}
\label{fig:hybrid}
\end{center}
\end{figure}

@@

\label{Bibliography}
\bibliographystyle{apsrev4-1}
%\bibliography{perovskites}

@@

%Control: author (8) initials jnrlst

@@

%Control: production of article title (-1) disabled
%Control: page (0) single
%Control: year (1) truncated

@@

\begin{thebibliography}{83}%

@@

  {Zubko}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Gariglio}},
  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Gabay}}, \bibinfo
  {author} {\bibfnamefont {P.}~\bibnamefont {Ghosez}}, \ and\ \bibinfo {author}
  {\bibfnamefont {J.-M.}\ \bibnamefont {Triscone}},\ }\href {\doibase

@@

  {volume} {2}},\ \bibinfo {pages} {141} (\bibinfo {year} {2011})}\BibitemShut

@@

  {\bibfnamefont {Y.}~\bibnamefont {Tokura}},\ }\href {\doibase
  10.1038/nmat3223} {\bibfield  {journal} {\bibinfo  {journal} {Nature
  Materials}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo {pages} {103}

@@

  {Bhattacharya}}\ and\ \bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont
  {May}},\ }\href {\doibase 10.1146/annurev-matsci-070813-113447} {\bibfield
  {journal} {\bibinfo  {journal} {Annual Review of Materials Research}\
  }\textbf {\bibinfo {volume} {44}},\ \bibinfo {pages} {65} (\bibinfo {year}
  {2014})},\ \Eprint

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
  {Hellman}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Hoffmann}},
  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Tserkovnyak}}, \bibinfo
  {author} {\bibfnamefont {G.~S.~D.}\ \bibnamefont {Beach}}, \bibinfo {author}
  {\bibfnamefont {E.~E.}\ \bibnamefont {Fullerton}}, \bibinfo {author}
  {\bibfnamefont {C.}~\bibnamefont {Leighton}}, \bibinfo {author}
  {\bibfnamefont {A.~H.}\ \bibnamefont {MacDonald}}, \bibinfo {author}
  {\bibfnamefont {D.~C.}\ \bibnamefont {Ralph}}, \bibinfo {author}
  {\bibfnamefont {D.~A.}\ \bibnamefont {Arena}}, \bibinfo {author}
  {\bibfnamefont {H.~A.}\ \bibnamefont {D\"urr}}, \bibinfo {author}
  {\bibfnamefont {P.}~\bibnamefont {Fischer}}, \bibinfo {author} {\bibfnamefont
  {J.}~\bibnamefont {Grollier}}, \bibinfo {author} {\bibfnamefont {J.~P.}\
  \bibnamefont {Heremans}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
  {Jungwirth}}, \bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont
  {Kimel}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Koopmans}},
  \bibinfo {author} {\bibfnamefont {I.~N.}\ \bibnamefont {Krivorotov}},
  \bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont {May}}, \bibinfo
  {author} {\bibfnamefont {A.~K.}\ \bibnamefont {Petford-Long}}, \bibinfo
  {author} {\bibfnamefont {J.~M.}\ \bibnamefont {Rondinelli}}, \bibinfo
  {author} {\bibfnamefont {N.}~\bibnamefont {Samarth}}, \bibinfo {author}
  {\bibfnamefont {I.~K.}\ \bibnamefont {Schuller}}, \bibinfo {author}
  {\bibfnamefont {A.~N.}\ \bibnamefont {Slavin}}, \bibinfo {author}
  {\bibfnamefont {M.~D.}\ \bibnamefont {Stiles}}, \bibinfo {author}
  {\bibfnamefont {O.}~\bibnamefont {Tchernyshyov}}, \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Thiaville}}, \ and\ \bibinfo {author}
  {\bibfnamefont {B.~L.}\ \bibnamefont {Zink}},\ }\href {\doibase

@@

  {Chen}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Millis}},\
  }\href {\doibase 10.1088/1361-648X/aa6efe} {\bibfield  {journal} {\bibinfo
  {journal} {Journal of Physics: Condensed Matter}\ }\textbf {\bibinfo {volume}
  {29}},\ \bibinfo {pages} {243001} (\bibinfo {year} {2017})}\BibitemShut

@@

  {Dagotto}},\ }\href {\doibase 10.1126/science.1107559} {\bibfield  {journal}
  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {309}},\ \bibinfo
  {pages} {257} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%

@@

  {Tokura}},\ }\href {\doibase 10.1557/mrs2008.223} {\bibfield  {journal}
  {\bibinfo  {journal} {MRS Bulletin}\ }\textbf {\bibinfo {volume} {33}},\
  \bibinfo {pages} {1037} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~B.}\ \bibnamefont
  {Salamon}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Jaime}},\ }\href {\doibase 10.1103/RevModPhys.73.583} {\bibfield  {journal}
  {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {73}},\
  \bibinfo {pages} {583} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%

@@

  {Ramesh}},\ }\href {\doibase 10.1126/science.1080615} {\bibfield  {journal}
  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {299}},\ \bibinfo
  {pages} {1719} (\bibinfo {year} {2003})},\ \Eprint

@@

  and\ \bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont {Scott}},\ }\href
  {\doibase 10.1103/RevModPhys.77.1083} {\bibfield  {journal} {\bibinfo
  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {77}},\ \bibinfo
  {pages} {1083} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~G.}\ \bibnamefont
  {Schlom}}, \bibinfo {author} {\bibfnamefont {L.-Q.}\ \bibnamefont {Chen}},
  \bibinfo {author} {\bibfnamefont {C.-B.}\ \bibnamefont {Eom}}, \bibinfo
  {author} {\bibfnamefont {K.~M.}\ \bibnamefont {Rabe}}, \bibinfo {author}
  {\bibfnamefont {S.~K.}\ \bibnamefont {Streiffer}}, \ and\ \bibinfo {author}
  {\bibfnamefont {J.-M.}\ \bibnamefont {Triscone}},\ }\href {\doibase

@@

  {37}},\ \bibinfo {pages} {589} (\bibinfo {year} {2007})}\BibitemShut

@@

  {Koster}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Klein}},
  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Siemons}}, \bibinfo
  {author} {\bibfnamefont {G.}~\bibnamefont {Rijnders}}, \bibinfo {author}
  {\bibfnamefont {J.~S.}\ \bibnamefont {Dodge}}, \bibinfo {author}
  {\bibfnamefont {C.-B.}\ \bibnamefont {Eom}}, \bibinfo {author} {\bibfnamefont
  {D.~H.~A.}\ \bibnamefont {Blank}}, \ and\ \bibinfo {author} {\bibfnamefont
  {M.~R.}\ \bibnamefont {Beasley}},\ }\href {\doibase

@@

  Mod. Phys.}\ }\textbf {\bibinfo {volume} {84}},\ \bibinfo {pages} {253}

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
  {Bersuker}},\ }\href {\doibase https://doi.org/10.1016/S0010-8545(00)80266-0}
  {\bibfield  {journal} {\bibinfo  {journal} {Coordination Chemistry Reviews}\
  }\textbf {\bibinfo {volume} {14}},\ \bibinfo {pages} {357} (\bibinfo {year}

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~I.}\ \bibnamefont
  {Kugel}}\ and\ \bibinfo {author} {\bibfnamefont {D.~I.}\ \bibnamefont
  {Khomski{\u i}}},\ }\href {\doibase 10.1070/PU1982v025n04ABEH004537}
  {\bibfield  {journal} {\bibinfo  {journal} {Soviet Physics Uspekhi}\ }\textbf
  {\bibinfo {volume} {25}},\ \bibinfo {pages} {231} (\bibinfo {year}
  {1982})}\BibitemShut {NoStop}%

@@

  {Millis}},\ }\href {\doibase 10.1038/32348} {\bibfield  {journal} {\bibinfo
  {journal} {Nature}\ }\textbf {\bibinfo {volume} {392}},\ \bibinfo {pages}
  {147} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%

@@

  {Terakura}},\ }\href {\doibase https://doi.org/10.1016/j.pmatsci.2006.10.007}

@@

  }\textbf {\bibinfo {volume} {52}},\ \bibinfo {pages} {388} (\bibinfo {year}
  {2007})},\ \bibinfo {note} {modelling electrons and atoms for materials
  science}\BibitemShut {NoStop}%

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
  {Halcrow}},\ }\href {\doibase 10.1039/C2CS35253B} {\bibfield  {journal}
  {\bibinfo  {journal} {Chemical Society Reviews}\ }\textbf {\bibinfo {volume}
  {42}},\ \bibinfo {pages} {1784} (\bibinfo {year} {2013})}\BibitemShut

@@

  {Lufaso}}\ and\ \bibinfo {author} {\bibfnamefont {P.~M.}\ \bibnamefont
  {Woodward}},\ }\href {\doibase 10.1107/S0108768103026661} {\bibfield

@@

  {\bibinfo {volume} {60}},\ \bibinfo {pages} {10} (\bibinfo {year}

@@

  {Glazer}},\ }\href {\doibase 10.1107/S0567740872007976} {\bibfield  {journal}
  {\bibinfo  {journal} {Acta Crystallogr., Sect. B: Struct. Crystallogr. Cryst.
  Chem.}\ }\textbf {\bibinfo {volume} {28}},\ \bibinfo {pages} {3384} (\bibinfo
  {year} {1972})}\BibitemShut {NoStop}%

@@

  {Thomas}},\ }\href {\doibase 10.1107/S0108768195006100} {\bibfield  {journal}
  {\bibinfo  {journal} {Acta Crystallographica Section B}\ }\textbf {\bibinfo

>>>>

\documentclass[a4paper,prb,twocolumn,longbibliography]{revtex4-1}  %a4paper,prb,twocolumn
%\documentclass[preprint]{revtex4-1}

@@

Of course, beside the crystal field we consider in our simplistic model,
in real materials,
 there would be other local effects like
electronic correlations (Hubbard and Hund's interaction)
and spin-orbit interaction, 
as well as band structure effects arising from
the electron hopping between the B ions.
The interplay between these and the crystal field (or JT) effect 
we discussed in this manuscript is also an interesting future work.
A discussion 
about the role of 
electron hopping 
along with some preliminary results 
follows.

Assuming the crystal field splitting to be the largest energy scale,
the orbitals in the $e_g$ and $t_{2g}$ manifolds of B sites are aligned with their respective octahedra.
The electron hopping between these orbitals that are 
localized on different B sites 
%(that creates electronic bands)
depends on the relative orientation of the orbitals.
As the octahedra rotate (or tilt),
the hybridization between the
neighboring sites
change,
modifying
the electronic bands and associated band energy.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.0\linewidth]{hybrid}
\caption{The effect of electron hopping between B sites.
(a) Energy of two configurations $t_{2g}^1$ and $e_g^1$
as a function of $\beta$ when either the crystal field or the hopping is considered alone.
In the latter case, the energy changes are scaled with the bandwidth $W$.
(b) Considering both the crystal field and the hopping simultaneously,
the ratio of the change in energy with rotation $\beta$ at a finite hopping to that in the absence of hopping $E(W)/E(0)$
as a function of the average bandwidth $W$, 
for the same two configurations
$t_{2g}^1$ and $e_g^1$.
The results of the crystal field model presented in this manuscript 
hold in the small bandwidth limit where $E(W)/E(0)\sim 1$.
}
\label{fig:hybrid}
\end{center}
\end{figure}

To shed some light on the 
role of these band structure effects,
we consider the nearest neighbor hopping between the B sites
using the Slater-Koster method~\cite{SlaterPR54}
and
calculate the change in the energy of 
the system
as the octahedra rotate.
We do this for three cases: with either the crystal field or the hopping only,
 and with both of these simultaneously.
%
Figure~\ref{fig:hybrid}(a)
shows the change in the energy 
of two (spinless) configurations $t_{2g}^1$ and $e_g^1$
as a function of $\beta$ for the first two cases
for the crystal-field-only (black curves, left y-axis;
$\alpha=0$, $q=2q_o$, $\Delta_o=4q_o/15a$)
and for the hopping-only case (red/gray curves, right y-axis).
We
use Slater-Koster hopping parameters
$(t_{\sigma},t_{\pi},t_{\delta})=(0.15,-0.1,0.025)$~eV, 
% W = \{0.0330745,0.0385869,0.0358307\} Hartree
% W = {0.900005, 1.05, 0.975004} eV
%$(t_{\sigma},t_{\pi},t_{\delta})/W= {0.153846, -0.102564, 0.0256409}$
$a=7$~bohr, $q_o=2$~e,
and consider only the crystal field of O octahedra that creates
$t_{2g}$ and $e_g$ manifolds.
(These parameters produce an average
bandwidth $W=0.97$~eV for the two manifolds).
While both $t_{2g}^1$ and $e_g^1$ configurations 
show a lowering of energy 
due to
the crystal field 
as $\beta$ 
increases---consistent with the results presented 
before---the energy of $e_g^1$ increases when only hopping is considered 
(the effect scales with the hopping parameters or the bandwidth).
This is due to a reduced hybridization leading to narrower $e_g$ bands.
In contrast, the energy of $t_{2g}^1$ decreases due to a band widening arising from 
an enhanced hybridization.
The crystal field and these band structure effects are not additive however.
The rotation induced splitting of the $t_{2g}$/$e_g$ manifolds
arising from the crystal field
suppresses the effectiveness of the hopping in creating 
the dispersion in the energy states, 
and thus reduces the bandwidths and the
the associated rotation induced energetic changes.

To show the validity regime of our crystal field model 
presented in this manuscript,
Fig.~\ref{fig:hybrid}(b)
presents  
the ratio of the
 change in the energy 
at $\beta=20^\circ$ (i.e., the energy difference from the cubic case)
at finite hopping $E(W)$ to that of our simplistic crystal field model $E(0)$
as a function of the average bandwidth $W$ of $t_{2g}$ and $e_g$ bands.
Here we scale the Slater-Koster parameters used for Fig.~\ref{fig:hybrid}(a)
to tune the bandwidth $W$.
We see that $E(W)/E(0)$ decreases from unity at $W=0$
to half its value for $t_{2g}^1$ configuration at $W/\Delta_o\gtrsim0.3$,
and even becomes negative for $e_g^1$ configuration around 
$W/\Delta_o\gtrsim0.15$ (showing the dominance of the band structure effects).
From this analysis, we conclude that the results of our crystal field model 
hold unambiguously only for narrower bands, $W/\Delta_o\ll1$,
while a detailed further study is required to understand the interplay of the two effects
at larger bandwidths.

@@

\label{Bibliography}
%\bibliographystyle{apsrev4-1}
%\bibliography{perovskites}

@@

%Control: author (0) dotless jnrlst

@@

%Control: production of article title (0) allowed
%Control: page (1) range
%Control: year (0) verbatim

@@

\begin{thebibliography}{84}%

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Pavlo}\ \bibnamefont
  {Zubko}}, \bibinfo {author} {\bibfnamefont {Stefano}\ \bibnamefont
  {Gariglio}}, \bibinfo {author} {\bibfnamefont {Marc}\ \bibnamefont {Gabay}},
  \bibinfo {author} {\bibfnamefont {Philippe}\ \bibnamefont {Ghosez}}, \ and\
  \bibinfo {author} {\bibfnamefont {Jean-Marc}\ \bibnamefont {Triscone}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {Interface physics in complex
  oxide heterostructures},}\ }\href {\doibase

@@

  {volume} {2}},\ \bibinfo {pages} {141--165} (\bibinfo {year}

@@

  {\bibfnamefont {Y.}~\bibnamefont {Tokura}},\ }\bibfield  {title} {\enquote
  {\bibinfo {title} {Emergent phenomena at oxide interfaces},}\ }\href
  {\doibase 10.1038/nmat3223} {\bibfield  {journal} {\bibinfo  {journal}
  {Nature Materials}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo {pages}
  {103--113} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Anand}\ \bibnamefont
  {Bhattacharya}}\ and\ \bibinfo {author} {\bibfnamefont {Steven~J.}\
  \bibnamefont {May}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {Magnetic oxide heterostructures},}\ }\href {\doibase
  10.1146/annurev-matsci-070813-113447} {\bibfield  {journal} {\bibinfo
  {44}},\ \bibinfo {pages} {65--90} (\bibinfo {year} {2014})},\ \Eprint

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Frances}\ \bibnamefont
  {Hellman}}, \bibinfo {author} {\bibfnamefont {Axel}\ \bibnamefont
  {Hoffmann}}, \bibinfo {author} {\bibfnamefont {Yaroslav}\ \bibnamefont
  {Tserkovnyak}}, \bibinfo {author} {\bibfnamefont {Geoffrey S.~D.}\
  \bibnamefont {Beach}}, \bibinfo {author} {\bibfnamefont {Eric~E.}\
  \bibnamefont {Fullerton}}, \bibinfo {author} {\bibfnamefont {Chris}\
  \bibnamefont {Leighton}}, \bibinfo {author} {\bibfnamefont {Allan~H.}\
  \bibnamefont {MacDonald}}, \bibinfo {author} {\bibfnamefont {Daniel~C.}\
  \bibnamefont {Ralph}}, \bibinfo {author} {\bibfnamefont {Dario~A.}\
  \bibnamefont {Arena}}, \bibinfo {author} {\bibfnamefont {Hermann~A.}\
  \bibnamefont {D\"urr}}, \bibinfo {author} {\bibfnamefont {Peter}\
  \bibnamefont {Fischer}}, \bibinfo {author} {\bibfnamefont {Julie}\
  \bibnamefont {Grollier}}, \bibinfo {author} {\bibfnamefont {Joseph~P.}\
  \bibnamefont {Heremans}}, \bibinfo {author} {\bibfnamefont {Tomas}\
  \bibnamefont {Jungwirth}}, \bibinfo {author} {\bibfnamefont {Alexey~V.}\
  \bibnamefont {Kimel}}, \bibinfo {author} {\bibfnamefont {Bert}\ \bibnamefont
  {Koopmans}}, \bibinfo {author} {\bibfnamefont {Ilya~N.}\ \bibnamefont
  {Krivorotov}}, \bibinfo {author} {\bibfnamefont {Steven~J.}\ \bibnamefont
  {May}}, \bibinfo {author} {\bibfnamefont {Amanda~K.}\ \bibnamefont
  {Petford-Long}}, \bibinfo {author} {\bibfnamefont {James~M.}\ \bibnamefont
  {Rondinelli}}, \bibinfo {author} {\bibfnamefont {Nitin}\ \bibnamefont
  {Samarth}}, \bibinfo {author} {\bibfnamefont {Ivan~K.}\ \bibnamefont
  {Schuller}}, \bibinfo {author} {\bibfnamefont {Andrei~N.}\ \bibnamefont
  {Slavin}}, \bibinfo {author} {\bibfnamefont {Mark~D.}\ \bibnamefont
  {Stiles}}, \bibinfo {author} {\bibfnamefont {Oleg}\ \bibnamefont
  {Tchernyshyov}}, \bibinfo {author} {\bibfnamefont {Andr\'e}\ \bibnamefont
  {Thiaville}}, \ and\ \bibinfo {author} {\bibfnamefont {Barry~L.}\
  \bibnamefont {Zink}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {Interface-induced phenomena in magnetism},}\ }\href {\doibase

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Hanghui}\ \bibnamefont
  {Chen}}\ and\ \bibinfo {author} {\bibfnamefont {Andrew}\ \bibnamefont
  {Millis}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Charge transfer
  driven emergent phenomena in oxide heterostructures},}\ }\href {\doibase
  10.1088/1361-648X/aa6efe} {\bibfield  {journal} {\bibinfo  {journal} {Journal
  of Physics: Condensed Matter}\ }\textbf {\bibinfo {volume} {29}},\ \bibinfo
  {pages} {243001} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Elbio}\ \bibnamefont
  {Dagotto}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Complexity in
  strongly correlated electronic systems},}\ }\href {\doibase
  10.1126/science.1107559} {\bibfield  {journal} {\bibinfo  {journal}
  {Science}\ }\textbf {\bibinfo {volume} {309}},\ \bibinfo {pages} {257--262}
  (\bibinfo {year} {2005})}\BibitemShut {NoStop}%

@@

  {Tokura}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Strongly
  correlated electronic materials: Present and future},}\ }\href {\doibase
  10.1557/mrs2008.223} {\bibfield  {journal} {\bibinfo  {journal} {MRS
  Bulletin}\ }\textbf {\bibinfo {volume} {33}},\ \bibinfo {pages} {1037--1045}
  (\bibinfo {year} {2008})}\BibitemShut {NoStop}%

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Myron~B.}\
  \bibnamefont {Salamon}}\ and\ \bibinfo {author} {\bibfnamefont {Marcelo}\
  \bibnamefont {Jaime}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {The
  physics of manganites: Structure and transport},}\ }\href {\doibase
  10.1103/RevModPhys.73.583} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
  Mod. Phys.}\ }\textbf {\bibinfo {volume} {73}},\ \bibinfo {pages} {583--628}
  (\bibinfo {year} {2001})}\BibitemShut {NoStop}%

@@

  {Ramesh}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Epitaxial
  bifeo<sub>3</sub> multiferroic thin film heterostructures},}\ }\href
  {\doibase 10.1126/science.1080615} {\bibfield  {journal} {\bibinfo  {journal}
  {Science}\ }\textbf {\bibinfo {volume} {299}},\ \bibinfo {pages} {1719--1722}
  (\bibinfo {year} {2003})},\ \Eprint

@@

  and\ \bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont {Scott}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {Physics of thin-film
  ferroelectric oxides},}\ }\href {\doibase 10.1103/RevModPhys.77.1083}
  {\bibfield  {journal} {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf
  {\bibinfo {volume} {77}},\ \bibinfo {pages} {1083--1130} (\bibinfo {year}
  {2005})}\BibitemShut {NoStop}%

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Darrell~G.}\
  \bibnamefont {Schlom}}, \bibinfo {author} {\bibfnamefont {Long-Qing}\
  \bibnamefont {Chen}}, \bibinfo {author} {\bibfnamefont {Chang-Beom}\
  \bibnamefont {Eom}}, \bibinfo {author} {\bibfnamefont {Karin~M}\ \bibnamefont
  {Rabe}}, \bibinfo {author} {\bibfnamefont {Stephen~K}\ \bibnamefont
  {Streiffer}}, \ and\ \bibinfo {author} {\bibfnamefont {Jean-Marc}\
  \bibnamefont {Triscone}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {Strain tuning of ferroelectric thin films},}\ }\href {\doibase

@@

  {37}},\ \bibinfo {pages} {589--626} (\bibinfo {year} {2007})}\BibitemShut

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Gertjan}\ \bibnamefont
  {Koster}}, \bibinfo {author} {\bibfnamefont {Lior}\ \bibnamefont {Klein}},
  \bibinfo {author} {\bibfnamefont {Wolter}\ \bibnamefont {Siemons}}, \bibinfo
  {author} {\bibfnamefont {Guus}\ \bibnamefont {Rijnders}}, \bibinfo {author}
  {\bibfnamefont {J.~Steven}\ \bibnamefont {Dodge}}, \bibinfo {author}
  {\bibfnamefont {Chang-Beom}\ \bibnamefont {Eom}}, \bibinfo {author}
  {\bibfnamefont {Dave H.~A.}\ \bibnamefont {Blank}}, \ and\ \bibinfo {author}
  {\bibfnamefont {Malcolm~R.}\ \bibnamefont {Beasley}},\ }\bibfield  {title}
  {\enquote {\bibinfo {title} {Structure, physical properties, and applications
  of ${\mathrm{srruo}}_{3}$ thin films},}\ }\href {\doibase

@@

  Mod. Phys.}\ }\textbf {\bibinfo {volume} {84}},\ \bibinfo {pages} {253--298}

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.B.}\ \bibnamefont
  {Bersuker}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {The
  {Jahn-Teller} effect in crystal chemistry and spectroscopy},}\ }\href
  {\doibase https://doi.org/10.1016/S0010-8545(00)80266-0} {\bibfield
  {journal} {\bibinfo  {journal} {Coordination Chemistry Reviews}\ }\textbf
  {\bibinfo {volume} {14}},\ \bibinfo {pages} {357--412} (\bibinfo {year}

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Kliment~I}\
  \bibnamefont {Kugel}}\ and\ \bibinfo {author} {\bibfnamefont {D~I}\
  \bibnamefont {Khomski{\u i}}},\ }\bibfield  {title} {\enquote {\bibinfo
  {title} {The jahn-teller effect and magnetism: transition metal compounds},}\
  }\href {\doibase 10.1070/PU1982v025n04ABEH004537} {\bibfield  {journal}
  {\bibinfo  {journal} {Soviet Physics Uspekhi}\ }\textbf {\bibinfo {volume}
  {25}},\ \bibinfo {pages} {231} (\bibinfo {year} {1982})}\BibitemShut

@@

  {Millis}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Lattice effects
  in magnetoresistive manganese perovskites},}\ }\href {\doibase 10.1038/32348}
  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
  {volume} {392}},\ \bibinfo {pages} {147--150} (\bibinfo {year}
  {1998})}\BibitemShut {NoStop}%

@@

  {Terakura}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Magnetism,
  orbital ordering and lattice distortion in perovskite transition-metal
  oxides},}\ }\href {\doibase https://doi.org/10.1016/j.pmatsci.2006.10.007}

@@

  }\textbf {\bibinfo {volume} {52}},\ \bibinfo {pages} {388--400} (\bibinfo
  {year} {2007})},\ \bibinfo {note} {modelling electrons and atoms for
  materials science}\BibitemShut {NoStop}%

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Malcolm~A.}\
  \bibnamefont {Halcrow}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {Jahn--teller distortions in transition metal compounds, and their importance
  in functional molecular and inorganic materials},}\ }\href {\doibase
  10.1039/C2CS35253B} {\bibfield  {journal} {\bibinfo  {journal} {Chemical
  Society Reviews}\ }\textbf {\bibinfo {volume} {42}},\ \bibinfo {pages}
  {1784--1795} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Michael~W.}\
  \bibnamefont {Lufaso}}\ and\ \bibinfo {author} {\bibfnamefont {Patrick~M.}\
  \bibnamefont {Woodward}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {{Jahn{--}Teller distortions, cation ordering and octahedral tilting in
  perovskites}},}\ }\href {\doibase 10.1107/S0108768103026661} {\bibfield

@@

  {\bibinfo {volume} {60}},\ \bibinfo {pages} {10--20} (\bibinfo {year}

@@

  {Glazer}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Classification
  of tilted octahedra in perovskites},}\ }\href {\doibase
  10.1107/S0567740872007976} {\bibfield  {journal} {\bibinfo  {journal} {Acta
  Crystallogr., Sect. B: Struct. Crystallogr. Cryst. Chem.}\ }\textbf {\bibinfo
  {volume} {28}},\ \bibinfo {pages} {3384} (\bibinfo {year}
  {1972})}\BibitemShut {NoStop}%

@@

  {Thomas}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{The
  compositional dependence of octahedral tilting in orthorhombic and tetragonal
  perovskites}},}\ }\href {\doibase 10.1107/S0108768195006100} {\bibfield
